---
title: "tracediff-analysis"
author: "Ruan Reis"
date: "4 de julho de 2017"
output: html_notebook
---

```{r setup, include=FALSE}

library(readr)
library(dplyr, warn.conflicts = F)
library(ggplot2)
library(resample)

data_experiment = read_csv("dados/TraceDiff- Experiments Data.csv")

data_survey = read_csv("dados/TraceDiff- Survey Data.csv")

```

```{r, echo=FALSE}

tracediff_data = data_experiment %>% 
  filter(condition == 'TD')

pythontutor_data = data_experiment %>% 
  filter(condition == 'PT')

```

## 1. Bugs solucionados

### 1.1 Intervalos de confiança 
```{r, echo=FALSE}

ggplot(data_experiment, aes(y = fixed_fault, x = condition)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  coord_flip()

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}

tracediff_fixed.mean =  bootstrap(tracediff_data, mean(fixed_fault)) %>% 
  CI.bca(probs = c(.025, .975))

pythontutor_fixed.mean =  bootstrap(pythontutor_data, mean(fixed_fault)) %>% 
  CI.bca(probs = c(.025, .975))

df = data.frame(rbind(tracediff_fixed.mean, 
                      pythontutor_fixed.mean))

df$`média` = c("TraceDiff", "Python Tutor")

df %>% 
  ggplot(aes(x = `média`, ymin = X2.5., ymax = X97.5.)) + 
  geom_errorbar(width = .2)

```

### 1.2 Diferença entre intervalos de confiança 

```{r, echo=FALSE}

fixed.diff.mean = bootstrap2(data_experiment$fixed_fault, 
                          treatment = data_experiment$condition, 
                          mean)

fixed.diff = CI.percentile(fixed.diff.mean, probs = c(.05, .95))

data.frame(fixed.diff) %>% 
  ggplot(aes(x = "Diferença", ymin = X5., ymax = X95.)) + 
  geom_errorbar(width = .2) + 
  geom_hline(yintercept = 0, colour = "darkorange")
```
**Diferença não é significativa**

### 1.3 P-value
```{r, echo=FALSE}
permutationTest2(data_experiment, mean(fixed_fault), treatment = condition)
```

## 2. Bugs identificados

### 2.1 Intervalos de confiança 
```{r, echo=FALSE}

ggplot(data_experiment, aes(y = identified_fault, x = condition)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  coord_flip()

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}

tracediff_identified.mean =  bootstrap(tracediff_data, mean(identified_fault)) %>% 
  CI.bca(probs = c(.025, .975))

pythontutor_identified.mean =  bootstrap(pythontutor_data, mean(identified_fault)) %>% 
  CI.bca(probs = c(.025, .975))

df = data.frame(rbind(tracediff_identified.mean, 
                      pythontutor_identified.mean))

df$`média` = c("TraceDiff", "Python Tutor")

df %>% 
  ggplot(aes(x = `média`, ymin = X2.5., ymax = X97.5.)) + 
  geom_errorbar(width = .2)

```

### 2.2 Diferença entre intervalos de confiança 

```{r, echo=FALSE}

identified.diff.mean = bootstrap2(data_experiment$identified_fault, 
                          treatment = data_experiment$condition, 
                          mean)

identified.diff = CI.percentile(identified.diff.mean, probs = c(.05, .95))

data.frame(identified.diff) %>% 
  ggplot(aes(x = "Diferença", ymin = X5., ymax = X95.)) + 
  geom_errorbar(width = .2) + 
  geom_hline(yintercept = 0, colour = "darkorange")
```
**Diferença não é significativa**

### 2.3 P-value
```{r, echo=FALSE}
permutationTest2(data_experiment, mean(identified_fault), treatment = condition)
```

## 3. Tempo

### 3.1 Intervalos de confiança 
```{r, echo=FALSE}

ggplot(data_experiment, aes(y = time, x = condition)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  coord_flip()

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}

tracediff_time.mean =  bootstrap(tracediff_data, mean(time)) %>% 
  CI.bca(probs = c(.025, .975))

pythontutor_time.mean =  bootstrap(pythontutor_data, mean(time)) %>% 
  CI.bca(probs = c(.025, .975))

df = data.frame(rbind(tracediff_time.mean, 
                      pythontutor_time.mean))

df$`média` = c("TraceDiff", "Python Tutor")

df %>% 
  ggplot(aes(x = `média`, ymin = X2.5., ymax = X97.5.)) + 
  geom_errorbar(width = .2)

```

### 3.2 Diferença entre intervalos de confiança 

```{r, echo=FALSE}

time.diff.mean = bootstrap2(data_experiment$time, 
                          treatment = data_experiment$condition, 
                          mean)

time.diff = CI.percentile(time.diff.mean, probs = c(.05, .95))

data.frame(time.diff) %>% 
  ggplot(aes(x = "Diferença", ymin = X5., ymax = X95.)) + 
  geom_errorbar(width = .2) + 
  geom_hline(yintercept = 0, colour = "darkorange")
```
**Diferença não é significativa**

### 3.3 P-value
```{r, echo=FALSE}
permutationTest2(data_experiment, mean(time), treatment = condition)
```